\documentclass{article}
\usepackage[rounded]{syntax}
\usepackage{url}

\title{Grammar for Language Describing Game Structures}
\author{Brooks MacLachlan}

\begin{document}
\maketitle

\noindent \textbf{Pretty-printed EBNF grammar:}
\begin{grammar}
<game> ::= <roundList> `played by' <teamList>

<teamList> ::= (<team> \{`,' <team>\} | <playerList> | `randomly divide' 
<playerList> `into' <nameList>) [`all' <attributeList>]

<team> ::= `team' <name> <playerList>

<playerList> ::= <player> \{`;' <player>\}

<player> ::= <name> <attributeList>

<attributeList> ::= <attribute> \{`,' <attribute>\}

<attribute> ::= <affiliation> | <score> | <resource>

<affiliation> ::= 'affiliated with' <name>

<score> ::= `score' <name> <number> 

<resource> ::= `resource' <name> <number>

<roundList> ::= <round> \{`;' <round>\} [<modifierList>]

<modifierList> ::= <modifier> \{`,' <modifier>\}

<modifier> ::= <roundReference> (`before' | `after') <phaseReference> `insert' 
<phase>

<roundReference> ::= `round' <number>

<phaseReference> ::= `phase' <number>

<round> ::= <phase> \{`,' <phase>\} [`repeated' <number> `times']

<phase> ::= <action> | <progression>

<action> ::= <competition> | <decision>

<competition> ::= [`scored' | `placed'] [`team'] `competition between' <idList>

<decision> ::= `vote by' <idList> `between' <idList> [`tiebroken by' 
<decision>] | 'nomination of' <number> 
`of' <idList> `by' <identifier> | `allocate' <resource> | `binary' %allocate 
%resources, 
%binary is for yes/no, up/down type decisions.

<progression> ::= (<affiliationUpdate> | <scoreUpdate>  | <resourceUpdate>) 
`for' <idList>

<affiliationUpdate> ::= `elimination' | (`add' | `remove') <affiliation> | 
[`evenly' | `number preserving'] `swap' <affiliationList> [`adding' 
<affiliationList>] | `change' <affiliation> `to' <affiliation>

<scoreUpdate> ::= (`increase' | `decrease') <score> `by' (<number> | 
<resultReference>) | `reset' <score>

<resourceUpdate> ::= (`gain' | `expend') <number> <resource> 

<idList> ::= <identifier> \{`,' <identifier>\} [`except' <idList>]

<identifier> ::= `everyone' | <name> | <affiliation> | <idReference> | `chance' 

<idReference> ::= <compReference> (`winner' | `loser') | <voteReference> 
(`majority' | `minority') `voted' | <allocationReference> `amount'

<compReference> ::= `competition' <number>

<voteReference> ::= `vote' <number>

<allocationReference> ::= `allocation' <number>

<name> ::= (`a' | ... | `z' | `A' | ... | `Z') \{`a' | ... | `z' | `A' | ... | 
`Z' | `0' | ... | `9'\}

<number> ::= (`0' | ... | `9')+

\end{grammar}

~\newline
Notes:
\begin{itemize}
	\item Allow for random decisions
	\item Vote tiebreakers?
	\item Win condition or update affiliation to winner for someone in last 
	round? Have a progression shortcut for win?
	\item make grammar unambiguous
	\item multiple votes? 
	\item I've restricted player attributes into 3 categories, with no 
	opportunity for customization outside those three. Am I okay with this?
	\item affiliation used everywhere, get syntax right
	\item score/resource include init number... maybe need separate 
	non-terminals for initializing attributes and referencing/updating 
	attributes
	\item should allocate be a decision and progression or just progression? 
	Probably just progression.
\end{itemize}
\end{document}